Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-12-08 ms.tex
retrieval results

\title{Global Climate of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations}

@@

\section{Retrieval}
We performed an atmospheric retrieval to determine the composition and thermal structure of the atmosphere of WASP-103b. We used the CHIMERA retrieval suite \citep{FIXME}, as well as. Briefly, the CHIMERA model fits for the atmospheric metallicity and carbon-to-oxygen ratio, assuming the atmosphere is in thermochemical equilibrium. The temperature-pressure profile is FIXME. We included opacity from the dominant absorbing species expected at the temperatures and pressures on WASP-103b, including FIXME. Previous analyses of emission spectra of the hottest planets have not included Hminus opacity, but we find that it has a significant effect on our results.

We also performed a simple grid search where we varied X.

\subsection{Thermal Inversion}

\subsection{Bond Albedo}

@@

\section{Discussion and Conclusions}

>>>>

\title{Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations}

@@

\section{Atmospheric Composition}
Since the phase-resolved spectra are consistent with blackbodies (except for the Spitzer 4.5 $\mu$m broadband photometry point), we opted for a simple grid-based retrieval of the planet's atmospheric properties, similar to the grid search used in Mansfield et al. and Arcangeli et al. (in prep). We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation (\textbf{Mike: elaborate}). The forward models compute self-consistent, radiative-convective temperature-pressure (T-P) profiles, and the molecular abundances are calculated in each atmospheric layer assuming thermochemical equilibrium.  We included opacity from the major absorbers expected for a hot Jupiter atmosphere (FIXME: Mike, what molecules are included?). Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates (FIXME: what temperatures?).  Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13} (FIXME: elaborate).

The best fit atmospheric metallicity is FIXME and 
The 68\% confidence interval for a

When we do not include H- opacity, FIXME what happens?

\subsection{Climate}
Heat redistribution, Bond albedo, inversions

%\subsection{Bond Albedo}

@@

\section{Discussion and Conclusions}
One-dimensional retrieval is probably wrong, since we showed the dayside may have a large temperature gradient -> should work on this in the future.

H- is important.

How does composition compare to other HJs.
